Monte Carlo and bootstrap for ALL parameters

### 2024-08-12 All_param.Rmd
Still a long way to go

    z0 <- mapply(function(one, long){qnorm(sum(long<one)/nboot)}, t(est_init),est_boot_val)

    u <- data.frame(x = numeric(), y = numeric())
    for(i in 1:n){
        x_i <- df_init[-i,]
        # u <- rbind(u, c(sum(x_i[3]/p), sum(x_i[4]/p)))
        u <- rbind(u, as.vector(mapply(function(j){mapply(sum(x_i[j]/p))}, 3:nb_var)))
    }
    # u <- cbind(u, mapply(function(x,y){x/y}, u[2], u[1]))
    u <- cbind(u, mapply(function(j){mapply(function(x,y){x/y}, u[j+4], u[j])}, 3:6) )
    uu <- as.data.frame( mapply(function(some_vec){mean(some_vec)-some_vec}, u) )
    acc <- mapply(function(some_vec){sum(some_vec**3)/(6*(sum(some_vec**2))^1.5)}, uu)

>>>>

    z0 <- mapply( function(j){qnorm(sum(mapply(function(long){long<est_init[,j]},est_boot_val[,j]))/nboot)} , 1:12) # length: nb_est
    # Same as: mapply(function(one, long){qnorm(sum(long<one)/nboot)}, t(est_init),est_boot_val)
      # qnorm(sum(mapply(function(one, long){long<one}, t(est_init),est_boot_val))/nboot)

    u <- data.frame(replicate(nb_var, numeric(0)))
    for(i in 1:n){
        x_i <- df_init[-i,]
        # u <- rbind(u, c(sum(x_i[3]/p), sum(x_i[4]/p)))
        u <- rbind(u, as.vector(mapply(function(j){sum(x_i[,j]/p)}, 3:(nb_var+2))))
    }
    # u <- cbind(u, mapply(function(x,y){x/y}, u[2], u[1]))
    u <- cbind(u, mapply(function(j){mapply(function(x,y){x/y}, u[j+4], u[j])}, 1:3) )
    uu <- as.data.frame( mapply(function(some_vec){mean(some_vec)-some_vec}, u) )
    acc <- mapply(function(some_vec){sum(some_vec**3)/(6*(sum(some_vec**2))^1.5)}, uu)
